Phosphatidyl diazirine alkyne alcohol

### 2025-07-29 IndividualStudies/AT_2025.qmd
Spent a long time learning about custom divs, applied a new one for cell types

---
title: "Thomas et al. 2025"
subtitle: "Trifunctional lipid derivatives: PE’s mitochondrial interactome"
date: 2024-12-26
format: 
  html:
    embed-resources: true
standalone: true
---
<!-- Data overview
Two lipid probes, PA and PE for a single cell line
 -->

@@

::: {.callout-tip}

## Membrane Fraction

@@

@@

:::{.callout-tip}

## Cytosolic Fraction

@@

>>>>

---
title: "Thomas et al. 2025"
subtitle: "Trifunctional lipid derivatives: PE’s mitochondrial interactome"
date: 2024-12-26
format: 
  html:
    embed-resources: false

standalone: false
---
<!-- Data overview
Two lipid probes, PA and PE for a single cell line
 -->

@@

:::{.cells collapse="true"}
::::{.cells-header}
Membrane Fraction
::::
::::{.cells-container}

@@

:::
::::
:::

<!-- 
### Gene Ontology Analysis

@@

:::{.cells collapse="true"}
::::{.cells-header}
Cytosolic Fraction
::::
::::{.cells-container}

@@

::::
:::

### 2025-07-29 LipidProbe/Glycosylphosphatidylinositol.qmd
Fixed GPI download link
Spent a long time learning about custom divs, applied a new one for cell types

---
title: "Bifunctional Glycosylphosphatidylinositol (GPI)"
prefer-html: true
format: 
  html:
    embed-resources: false
callout-icon: false
---

@@

{{< downloadthis LipidProbe/DataSets/bf-GPI_SK_2024_ChemEuro.csv dname="bf-GPI_SK_2024_ChemEuro">}}

>>>>

---
title: "Bifunctional Glycosylphosphatidylinositol (GPI)"
prefer-html: true
format: 
  html:
    embed-resources: false
---

@@

{{< downloadthis DataSets/bf-GPI_SK_2024_ChemEuro.csv dname="bf-GPI_SK_2024_ChemEuro">}}

### 2025-07-29 LipidProbe/Sphinganine.qmd
found some text issues in the plot legends, now fixed
Spent a long time learning about custom divs, applied a new one for cell types

---
title: "Trifunctional Sphinganine"
format: 
  html:
    embed-resources: false
callout-icon: false
---

@@

>>>>

---
title: "Trifunctional Sphinganine"
format: 
  html:
    embed-resources: false
---

@@

```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Farley et al., 2024](/IndividualStudies/SF_2024.qmd). MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).  Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."

### 2025-07-29 LipidProbe/Sphingosine.qmd
Spent a long time learning about custom divs, applied a new one for cell types

---
title: "Trifunctional Sphingosine"
format: 
  html:
    embed-resources: false
callout-icon: false
---

@@

:::: {.callout-tip}

### Cell background: Huh7

@@

::::

:::: {.callout-tip}

### Cell background: HeLa

@@

::::

>>>>

---
title: "Trifunctional Sphingosine"
format: 
  html:
    embed-resources: false
---

@@

:::{.cells collapse="true"}
::::{.cells-header}
Cell background: Huh7
::::
::::{.cells-container}

@@

::::
:::

:::{.cells collapse="true"}
::::{.cells-header}
Cell background: HeLa
::::
::::{.cells-container}

@@

**\*Data presentation still in development.**

::::
:::

### 2025-07-29 _site/LipidProbe/PhosphatidylAlcohol.qmd
Spent a long time learning about custom divs, applied a new one for cell types

---
title: "Phosphatidyl diazirine alkyne alcohol"
subtitle: "PDAA"
format: 
  html:
    embed-resources: false
callout-icon: false
---

@@

```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Yu et al., 2021](/IndividualStudies/WY_2021.qmd). Black proteins are designated as not statistically significant. Orange \"enriched hit\" denotes proteins with fold-changes > 1.5 (logFC > 0.5) pvalue < 0.05. Only proteins identified in all three replicates are displayed."

>>>>

---
title: "Phosphatidyl diazirine alkyne alcohol"
subtitle: "PDAA"
format: 
  html:
    embed-resources: false
---

@@

```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Yu et al., 2021](/IndividualStudies/WY_2021.qmd). MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).  Black proteins are designated as not statistically significant. Orange \"enriched hit\" denotes proteins with fold-changes > 1.5 (logFC > 0.5) pvalue < 0.05. Only proteins identified in all three replicates are displayed."
